Lossy compression of DNA sequencing quality data

### 2015-02-06 manuscript/q-compression.tex
a few small changes

\section{Results:}
Lossy compression of quality information can greatly decrease storage
and memory requirements with little discernable effects on subsequent
analysis results. The four compression strategies in this study were
able to produce similar results to those obtained with uncompressed
quality sequences in terms of quality control, genome assembly, and
alignment of short read to a reference sequence.

>>>>

\section{Results:}
Lossy compression of quality information can greatly decrease storage
and memory requirements with little discernible effects on subsequent
analysis results. The four compression strategies in this study were
able to produce similar results to those obtained with uncompressed
quality sequences in terms of quality control, genome assembly, and
alignment of short read to a reference sequence.
